Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-24 manuscript.tex
minor change

Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
\begin{equation}
    \rbM \dot\fe
    =
    -\rbVm \fe
    -\mm K \fe
    + \mv f
    -\rbd + \mysat(\rbu)
    ,
    \label{eq:sys:filtered}
\end{equation}
where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
    =
    \mm K \fe
    +\rbM(-\ddqd+\mm\Lambda\dot{\mv e})
    +
    \rbVm(-\dqd+\mm\Lambda\mv e)
    -
    \rbF
    -
    \rbG
    \in\R^n
$ denotes the lumped system uncertainty.

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \act_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!proposed\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_i$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig9.eps
        }%
    \caption{
        Computational time of CONAC and CONAC-AUX. 
    }
    \label{fig:ctrl:real:result:cmp:time}
  \end{figure}

>>>>

Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
\begin{equation}
    \rbM \dot\fe
    =
    -\rbVm \fe
    -\mm K \fe
    + \mv f
    -\rbd + \mysat(\rbu)
    ,
    \label{eq:sys:filtered}
\end{equation}
where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
    \mv f:= \mv f(\q,\dq,\qd,\dqd,\ddqd)
    =
    \mm K \fe
    +\rbM(-\ddqd+\mm\Lambda\dot{\mv e})
    +
    \rbVm(-\dqd+\mm\Lambda\mv e)
    -
    \rbF
    -
    \rbG
    \in\R^n
$ denotes the lumped system uncertainty.

@@

The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \act_i(\NN_{i-1}), 
        &
        i\in\{1,\dots,k\},
        \\
        \wV_0^\top {\q}_n,
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
        }_{=:c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{=: c_2 \in\R_{>0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

% \begin{table}[t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
%     \centering
%     \begin{tabular}{c m{9.5em} c c c }
%     % \begin{tabular}{c c c c c}
%     \hline
%     \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
%     \hline
%     \hline 
%     $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
%     \hline
%     $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
%     \hline
%     ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
%     \hline
%     $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
%     \hline
%     ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
%     \hline
%     ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
%     \hline
%     $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
%     \hline
%     \end{tabular}
%     \label{table:system:params}
% \end{table}

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

\begin{figure}[t]
    \centering
        \includegraphics[width=\figSizeOneCol\linewidth]
        {
            src/measurement/figures/Fig10.eps
        }%
    \caption{
        Computational time of CONAC and CONAC-AUX. 
    }
    \label{fig:ctrl:real:result:cmp:time}
  \end{figure}
